\documentclass[a4paper, sans]{moderncv}
\usepackage[9pt]{extsizes}

% ModernCV Settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[scale=0.85]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontspec}

\setmainfont{IBMPlexSans}

\setlist[itemize]{noitemsep, topsep=0pt}
\setlength{\multicolsep}{2pt}

\moderncvtheme{fancy}
\moderncvcolor{grey}
\setlength{\hintscolumnwidth}{4.5cm}
\nopagenumbers{}


\colorlet{languagecolor}{red}
\colorlet{nolanguagecolor}{gray}
\newcount\languagecount
\newcommand\languageknowledge[2]
{%
    \hbox
    {%
        \makebox[1.5cm][l]{#1}%
        \languagecount=0
    \loop\ifnum\languagecount<#2
    \advance\languagecount1
    \textcolor{languagecolor}{$\bullet$}%
    \repeat
    \loop\ifnum\languagecount<5
    \advance\languagecount1
    \textcolor{nolanguagecolor}{$\bullet$}%
    \repeat
    }%
}


% Personal Information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\name{Jackson}{Campolattaro}

\address{Aan't Verlaat 33D}{Delft, Zuid-Holland}{2612XW, NL}
\email{jackson.campolattaro@gmail.com}
\phone[mobile]{+31 6 3030 7107}
\social[linkedin]{jacksoncampolattaro}
\social[github]{JacksonCampolattaro}
\extrainfo{jackson.campolattaro.nl}

\quote{
    Self-motivated Computer Engineering student
    with programming experience and an enthusiasm for Open Source principles.
    I'm currently seeking a software-focused thesis position in the Netherlands,
    with intentions to stay after my graduation.
}

\renewcommand*\namefont{\fontspec{IBMPlexSans}\fontsize{34}{36}\selectfont}
\renewcommand*\titlefont{\fontspec{IBMPlexSans}\fontsize{15}{18}\selectfont}
\renewcommand*\addressfont{\fontspec{IBMPlexSans}\fontsize{7}{9}\selectfont}
\renewcommand*\sectionfont{\fontspec{IBMPlexSans}\fontsize{12}{14}\selectfont}
\renewcommand*\subsectionfont{\fontspec{IBMPlexSans}\fontsize{10}{12}\selectfont}
\renewcommand*\quotefont{\fontspec{IBMPlexSans}\fontsize{9}{11}\selectfont}

% Document Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

    \makecvtitle


    \section{Education}
    \cventry{Fall 2021--Spring 2023}{TU Delft}{Computer Engineering}{}{}{
        Research-oriented masters in Computer Engineering, with a focus on software and software/hardware codesign.
    }
    \cventry{Fall 2018--Spring 2021}{Virginia Polytechnic}{Computer Engineering}{}{}{
        Major in Computer Engineering with a minor and specialization in Computer Science.
        Graduated 1 year early due to accelerated classes, GPA 3.64/4.00 in-major, 3.46/4.00 overall.
    }


    \section{Skills}

    \subsection{Languages}
    \cventry{8 Years Experience}{C++}{}{}{}{
    %Multithreading, Multiprocessor, Low-latency computing, Template Metaprogramming
        Libraries:
        Catch2, libsigc++, OpenMP, Intel TBB, Posix Threads,
        Gtkmm, Qt, OpenGL, GLFW, Magnum, CLI11, spdlog,
        Cereal, RapidJSON, TOML11, Libsoundio, FFTW
    }
    \cventry{5 Years Experience}{C, Python, Java}{}{}{}{
    %Multiprocessor, Real-time systems
        Libraries:
        Jansson, LibJWT
    }
    \cventry{In Order of Experience}{Others}{}{}{}{
        Rust, CUDA, Verilog, HTML + CSS/Sass, Octave/Matlab, MIPS Assembly, x86 Assembly
    }

    \subsection{Tools}
    \cvitem{}{
        \begin{multicols}{4}
            \begin{itemize}
                \item[] Git
                \item[] Linux
                \item[] Valgrind
                \item[] GDB
                \item[] Perf
                \item[] Tensorflow
                \item[] Travis CI
                \item[] Github Actions
                \item[] Ansible
                \item[] Doxygen
                \item[] Markdown
                \item[] \LaTeX
            \end{itemize}
        \end{multicols}
    }


    \section{Experience}

    \subsection{Employment}
    \cventry{May 2021--August 2021}{SIMD Research Internship}{Inria}{}{}{
        Worked alongside PhD students at Inria Research Center Sophia Antipolis to incorporate SIMD concepts into CGALs
        collision detection packages, improving performance.
    }
    \cventry{May 2020--August 2020}{Google Summer of Code Apprentice}{CGAL}{}{}{
        Worked remotely with a mentor in France to develop a new software package.
        The project is an Octree data structure, used in other packages.
        Required a mix of working with legacy code and green-field development.
    }
    \cventry{June 2019--August 2019}{Innovation Committee Member}{Telos Corp}{}{}{
        Worked in a 7 person group of interns
        researching the viability of future software security products.
        Built the frontend of a replacement for Telos’ employee intranet solution.
    }

    \subsection{Projects}
    \cventry{August 2020--June 2021}{Quarter ID}{Python}{}{}{
        Lead a small team of interdisceplenary engineering students
        to develop a solution which determines the value of collectible coins using machine vision.
        Involved industrial imaging and lighting hardware, paired with bespoke software written in Python using OpenCV.
    }
    \cventry{July 2018--Present}{N-Body}{C++}{}{}{
        Independently building a multi-threaded dynamical simulation tool to improve my
        familiarity with optimization, build tools, design patterns, and libraries.
        Incorporated concepts including concurrency, event-driven programming,
        serialization, cache-optimization, and tree algorithms among others.
    }
    \cventry{August 2020--December 2020}{Spectrogram}{C++}{}{}{
        Developed a low-latency Spectrogram audio frequency visualizer alongside two other students.
        Involved navigating real-time limitations in a contemporary event-driven desktop application,
        as well as CI, build system engineering, and other team management logistics.
    }

%\section{References}
%\cventry{\emailsymbol simon.giraudot@geometryfactory.com}{Dr. Simon Giraudot}{}{}{}{}
%\cventry{\emailsymbol crjones4@vt.edu}{Dr. Creed Jones}{}{}{}{}
%\cventry{\emailsymbol dmcphers@vt.edu}{Professor David McPherson}{}{}{}{}

\end{document}

